---
title: "Leafminer dfoliatR figures"
author: "Camilla Seirup"
date: "12/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r deps, include = FALSE}
library(tidyverse)
library(dplR)
library(dfoliatR)
```


```{r compile_data, include = FALSE}
source("leafminer_compile.R")
```

Chronologies as .pdfs in chrono_graphs folder

dfoliatR first attempt: defoliatation events by tree

```{r PEF tree defol, warning=FALSE, echo=FALSE, out.height="100%", fig.height= 7.5}
plot_defol(pLM_defol)
```

Figure 1. Defoliation events in THOC at the PEF



```{r Howland tree defol, warning=FALSE, echo=FALSE, out.height="100%", fig.height= 6.5}
plot_defol(hLM_defol)
```

Figure 2. Defoliation events in THOC at Howland



```{r ANP tree defol, warning=FALSE, echo=FALSE, out.height="100%", fig.height= 6.0}
plot_defol(aLM_defol)
```

Figure 3. Defoliation events in THOC at ANP



```{r BAS defol, warning=FALSE, echo=FALSE, out.height="100%", fig.height= 4.0}
plot_defol(bLM_defol)
```

Figure 4. Defoliation events in THOC at BAS



```{r PEF outbreak, warning=FALSE, echo=FALSE, out.height="100%", fig.height= 7}
plot_outbreak(pLM_outbr)
```
Figure 5. Outbreak results for THOC at the PEF



```{r Howland outbreak, warning=FALSE, echo=FALSE, out.height="100%", fig.height= 7}
plot_outbreak(hLM_outbr)
```

Figure 6. Outbreak results for THOC at the Howland



```{r ANP outbreak, warning=FALSE, echo=FALSE, out.height="100%", fig.height= 7}
plot_outbreak(aLM_outbr)
```

Figure 7. Outbreak results for THOC at the ANP



```{r BAS outbreak, warning=FALSE, echo=FALSE, out.height="100%", fig.height= 7}
plot_outbreak(bLM_outbr)
```

Figure 8. Outbreak results for THOC at the BAS


